### 2022-04-30 draft.tex
Deploying to gh-pages from @ EcoComplex/TrophicResourcesEdaphic@6b838c53f4e1c9c0cabdcb558234afdb37463bbb 🚀

\begin{figure}
\centering
\includegraphics[width=4.14in,height=\textheight]{figures/Metodo_ByTaxLevel.png}
\caption{Methods used in the literature to assign trophic resources to
soil mesofauna taxa. Colors within columns refer to the number of
different taxonomic levels for which each method assigned at least one
resource. Assay: laboratory tests and observations. Isotopes: stable
isotopes. Gut: intestinal content. Enzymes: Digestive enzymes. Mouth:
mouthparts morphology. Lipid: lipid profile. Mo. det: molecular
detection of intestinal content, f.p.: Food preference assays. Obs.:
direct lab observations of feeding activity. Reviews: general reviews by
other authors.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=5.7in,height=\textheight]{figures/Recursos_ByMetodo.png}
\caption{The number of records in the literature assigning each one of
the 13 trophic resources to a mesofauna taxon as shown in Table 1.
Colors in the columns refer to the method used to assign those trophic
resources to a particular taxon. Methods as in Fig. 2.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=5.4in,height=3.6in]{figures/Bi_Orden_Recurso.png}
\caption{Bipartite graph showing the use of trophic resources by the
main orders of Acari and Collembola. Upper nodes: Acari and Collembola
orders as in Table 2. Lower nodes: trophic resources. The thickness and
intensity of the lines give an idea of the proportion of mentions in the
available literature about their use of trophic resources. Resource
names as in Tables 1 and 2.}
\end{figure}

@@

Behan-Pelletier V, Newton G., 1999. Linking soil biodiversity and
ecosystem function. The taxonomic dilemma. BioScience 2.
\href{https://doi.org/10.2307/1313540}{{[}https://doi.org/10.2307/1313540{]}}.

Bellinger PF, Christiansen KA, Janssens F., 2020. Internet resource
available from:
\href{http://www.collembola.org/}{{[}http://www.collembola.org{]}}. Last
updated: November 30, 2020. Last accessed: December 23, 2020.

Berg, M.P., Stoffer, M., van den Heuvel, H. 2004. Feeding guilds in
Collembola based on digestive enzymes. Pedobiologia 48, 589-601. DOI:
\href{http://dx.doi.org/10.1016\%2Fj.pedobi.2004.07.006}{{[}\textbackslash10.1016/j.pedobi.2004.07.006{]}}

@@

\newpage
\blandscape

@@

\elandscape

>>>>

\begin{figure}
\centering
\includegraphics{figures/Metodo_ByTaxLevel.png}
\caption{Methods used in the literature to assign trophic resources to
soil mesofauna taxa. Colors within columns refer to the number of
different taxonomic levels for which each method assigned at least one
resource. Assay: laboratory tests and observations. Isotopes: stable
isotopes. Gut: intestinal content. Enzymes: Digestive enzymes. Mouth:
mouthparts morphology. Lipid: lipid profile. Mo. det: molecular
detection of intestinal content, f.p.: Food preference assays. Obs.:
direct lab observations of feeding activity. Reviews: general reviews by
other authors.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{figures/Recursos_ByMetodo.png}
\caption{The number of records in the literature assigning each one of
the 13 trophic resources to a mesofauna taxon as shown in Table 1.
Colors in the columns refer to the method used to assign those trophic
resources to a particular taxon. Methods as in Fig. 2.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{figures/Bi_Orden_Recurso.png}
\caption{Bipartite graph showing the use of trophic resources by the
main orders of Acari and Collembola. Upper nodes: Acari and Collembola
orders as in Table 2. Lower nodes: trophic resources. The thickness and
intensity of the lines give an idea of the proportion of mentions in the
available literature about their use of trophic resources. Resource
names as in Tables 1 and 2.}
\end{figure}

@@

Behan-Pelletier V, Newton G., 1999. Linking soil biodiversity and
ecosystem function. The taxonomic dilemma. BioScience 2.
\url{https://doi.org/10.2307/1313540}.

Bellinger PF, Christiansen KA, Janssens F., 2020. Internet resource
available from: \url{http://www.collembola.org}. Last updated: November
30, 2020. Last accessed: December 23, 2020.

Berg, M.P., Stoffer, M., van den Heuvel, H. 2004. Feeding guilds in
Collembola based on digestive enzymes. Pedobiologia 48, 589-601. DOI:
\href{http://dx.doi.org/10.1016\%2Fj.pedobi.2004.07.006}{10.1016/j.pedobi.2004.07.006}

@@

@@
